
---
title: "Government Censorship Analysis"
output: html_document
---

```{r setup, include=FALSE}
# Load required packages
p_needed <- c("viridis", "stargazer", "dplyr", "optimx", "MASS", "separationplot", "haven", "dagitty", "scales", "readxl", "mvtnorm")
packages <- rownames(installed.packages())
p_to_install <- p_needed[!(p_needed %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_needed, require, character.only = TRUE)
```

## 📂 Data Loading & Preparation

```{r load-data}
# Load dataset (replace with your local path if needed)
raw_data <- readxl::read_excel("data/censorship_data.xlsx")
df <- as.data.frame(raw_data)


# Convert relevant columns to numeric
df$cabinet_rl <- as.numeric(df$cabinet_rl)
df$parliament_rw <- as.numeric(df$parliament_rw)
df$gov_appr <- as.numeric(df$gov_appr)
df$terrorism_index <- as.numeric(df$terrorism_index)
df$gdp <- log(df$`GDP per Capita`)
```

## 📊 Modeling: Ideology Effects on Takedown Requests

### Model 1: Base model with ideology variables

```{r model-1}
m1 <- glm(dlt_req ~ cabinet_rl + parliament_rw, data = na.omit(df), family = "poisson")
summary(m1)

m2 <- glm.nb(dlt_req ~ cabinet_rl + parliament_rw, data = na.omit(df), control = glm.control(maxit = 100))
summary(m2)

# Likelihood Ratio Test for model comparison
L1 <- logLik(m1)
L2 <- logLik(m2)
LRT <- -2 * L1 + 2 * L2
LRT > qchisq(0.95, df = 1)
```

### Model 2: Add Government Approval Rate

```{r model-2}
m3 <- glm(dlt_req ~ cabinet_rl + parliament_rw + gov_appr, data = na.omit(df), family = "poisson")
summary(m3)

m4 <- glm.nb(dlt_req ~ cabinet_rl + parliament_rw + gov_appr, data = na.omit(df), control = glm.control(maxit = 100))
summary(m4)
```

### Model 3: Full Model with Controls

```{r model-3}
m5 <- glm(dlt_req ~ parliament_rw + cabinet_rl + gov_appr + terrorism_index + gdp, data = na.omit(df), family = "poisson")
summary(m5)

m6 <- glm.nb(dlt_req ~ parliament_rw + cabinet_rl + gov_appr + terrorism_index + gdp, data = na.omit(df), control = glm.control(maxit = 100))
summary(m6)
```

## 📋 Regression Summary Table

```{r regression-table, results='asis'}
stargazer(m2, m4, m6,
          title = "Regression Table for Models",
          dep.var.caption = c("Dependent Variable: Removal Requests"),
          dep.var.labels = "",
          column.labels = c("Model 1", "Model 2", "Model 3"),
          covariate.labels = c("Government ideology (right-left)", 
                               "Right-wing seat share in the parliament", 
                               "Approval rate of the government", 
                               "Terrorism scale", 
                               "GDP per capita", 
                               "Constant"))
```

## 📈 Scenario Simulation (Interpretation)

```{r simulation}
set.seed(1234)

# Simulation from the final model
nsim <- 1000
gamma_hat <- coef(m6)
V_hat <- vcov(m6)
S <- mvtnorm::rmvnorm(nsim, gamma_hat, V_hat)

# Example Scenario: Right-wing government
scenario1 <- cbind(
  1,
  mean(df$parliament_rw, na.rm = TRUE),
  1,
  mean(df$gov_appr, na.rm = TRUE),
  mean(df$terrorism_index, na.rm = TRUE),
  mean(df$gdp, na.rm = TRUE)
)

# Predicted counts for scenario
predicted_counts <- exp(scenario1 %*% t(S))
summary(predicted_counts)
```

## 🧠 Notes
- This analysis is part of a broader project. All data work, modeling, and interpretation here were done independently.
